Projection variability of clausal complements across different operators

### 2023-09-18 talks/XPrag-poster/xprag-poster.tex
abbreviated references further (names)

				\textbf{Márta Abrusán}. Predicting the presuppositions of soft triggers. \textit{L\&P}, 2011.\quad\textbullet\quad
				%
				\textbf{Gennaro Chierchia and Sally McConnell-Ginet.} \textit{Meaning and grammar: An introduction to semantics.} 1990.\quad\textbullet\quad
				%
				\textbf{Elizabeth Coppock and Lucas Champollion.} \textit{Invitation to formal semantics.} 2020.\quad\textbullet\quad
				%
				\textbf{Marie de Marneffe, Mandy Simons, and Judith Tonhauser.} The CommitmentBank: Investigating projection in naturally occurring discourse. \textit{SuB}, 2019.\quad\textbullet\quad
				%
				\textbf{Marie-Catherine de Marneffe, Christopher D. Manning, and Christopher Potts.} Did It Happen? The Pragmatic Complexity of Veridicality Assessment. \textit{Comp. Ling.}, February 2012.\quad\textbullet\quad
				%
				\textbf{Judith Degen and Judith Tonhauser.} Prior beliefs modulate projection. \textit{Open Mind}, 2021.\quad\textbullet\quad
				%
				\textbf{Judith Degen and Judith Tonhauser.} Are there factive predicates? An empirical investigation. \textit{Language}, 2022.\quad\textbullet\quad
				%
				\textbf{Kajsa Djärv and Hezekiah Akiva Bacovcin.} Prosodic effects on factive presupposition projection. \textit{SALT}, 2017.\quad\textbullet\quad
				%
				\textbf{Tom Roberts.} I can’t believe it’s not lexical: Deriving distributed veridicality. Semantics and Linguistic Theory, \textit{SALT}, 2019.\quad\textbullet\quad
				%
				\textbf{Gottlob Frege.} Über Sinn und Bedeutung. \textit{Zeitschrift für Philosophie und philosophische Kritik}, 1892.\quad\textbullet\quad
				%
				\textbf{Irene Heim.} Presupposition projection and the semantics of attitude verbs. \textit{JoS},1992.\quad\textbullet\quad
				%
				\textbf{Lauri Karttunen.} Some observations on factivity. \textit{Research on Language \& Social Interaction}, 1971.\quad\textbullet\quad
				%
				\textbf{Lauri Karttunen and Stanley Peters.} Conventional implicature. In Choon-Kyu Oh and David A. Dinneen, eds., \textit{Presuppositions, Syntax and Semantics}, 1979.\quad\textbullet\quad
				%
				\textbf{Paul Kiparsky and Carol Kiparsky.} Fact. In Manfred Bierwisch and Karl Erich Heidolph, eds., \textit{Progress in Linguistics}, 1970.\quad\textbullet\quad
				%
				\textbf{Taylor Mahler.} The social component of projection behavior of clausal complements. \textit{LSA}, 2020.\quad\textbullet\quad
				%
				\textbf{Philippe Schlenker.} Triggering presuppositions. \textit{Glossa}, 2021.\quad\textbullet\quad
				%
				\textbf{Judith Sieker and Torgrim Solstad.} Projective variability of (semi) factive verbs in family of sentence contexts: A rating study. \textit{AC 23}, 2022.\quad\textbullet\quad
				%
				\textbf{Mandy Simons, David Beaver, Craige Roberts, and Judith Tonhauser.} The best question: Explaining the projection behavior of factives. \textit{Discourse processes}, 2017.\quad\textbullet\quad
				%
				\textbf{E. Allyn Smith and Kathleen Currie Hall.} The relationship between projection and embedding environment. \textit{CLS 48}. 2014.\quad\textbullet\quad
				%
				\textbf{Peter F. Strawson.} On referring. \textit{Mind}, 1950.\quad\textbullet\quad
				%
				\textbf{Judith Tonhauser.} Prosodic cues to presupposition projection. In \textit{SALT}, 2016.\quad\textbullet\quad
				%
				\textbf{Judith Tonhauser, David I. Beaver, and Judith Degen.} How projective is projective content? Gradience in projectivity and at-issueness. \textit{JoS}, 2018.\quad\textbullet\quad
				%
				\textbf{Rob A. van der Sandt.} Presupposition projection as anaphora resolution. \textit{JoS}, 1992.

>>>>

				\textbf{M. Abrusán}. Predicting the presuppositions of soft triggers. \textit{L\&P}, 2011.\quad\textbullet\quad
				%
				\textbf{G. Chierchia and S. McConnell-Ginet.} \textit{Meaning and grammar: An introduction to semantics.} 1990.\quad\textbullet\quad
				%
				\textbf{E. Coppock and L. Champollion.} \textit{Invitation to formal semantics.} 2020.\quad\textbullet\quad
				%
				\textbf{M.-C. de Marneffe, M. Simons, and J. Tonhauser.} The CommitmentBank: Investigating projection in naturally occurring discourse. \textit{SuB}, 2019.\quad\textbullet\quad
				%
				\textbf{M.-C. de Marneffe, C.D. Manning, and C. Potts.} Did It Happen? The Pragmatic Complexity of Veridicality Assessment. \textit{Comp. Ling.}, February 2012.\quad\textbullet\quad
				%
				\textbf{J. Degen and J. Tonhauser.} Prior beliefs modulate projection. \textit{Open Mind}, 2021.\quad\textbullet\quad
				%
				\textbf{J. Degen and J. Tonhauser.} Are there factive predicates? An empirical investigation. \textit{Language}, 2022.\quad\textbullet\quad
				%
				\textbf{K. Djärv and H.A. Bacovcin.} Prosodic effects on factive presupposition projection. \textit{SALT}, 2017.\quad\textbullet\quad
				%
				\textbf{T. Roberts.} I can’t believe it’s not lexical: Deriving distributed veridicality. Semantics and Linguistic Theory, \textit{SALT}, 2019.\quad\textbullet\quad
				%
				\textbf{G. Frege.} Über Sinn und Bedeutung. \textit{Zeitschrift für Philosophie und philosophische Kritik}, 1892.\quad\textbullet\quad
				%
				\textbf{I. Heim.} Presupposition projection and the semantics of attitude verbs. \textit{JoS},1992.\quad\textbullet\quad
				%
				\textbf{L. Karttunen.} Some observations on factivity. \textit{Research on Language \& Social Interaction}, 1971.\quad\textbullet\quad
				%
				\textbf{L. Karttunen and S. Peters.} Conventional implicature. In Choon-Kyu Oh and David A. Dinneen, eds., \textit{Presuppositions, Syntax and Semantics}, 1979.\quad\textbullet\quad
				%
				\textbf{P. Kiparsky and C. Kiparsky.} Fact. In Manfred Bierwisch and Karl Erich Heidolph, eds., \textit{Progress in Linguistics}, 1970.\quad\textbullet\quad
				%
				\textbf{T. Mahler.} The social component of projection behavior of clausal complements. \textit{LSA}, 2020.\quad\textbullet\quad
				%
				\textbf{P. Schlenker.} Triggering presuppositions. \textit{Glossa}, 2021.\quad\textbullet\quad
				%
				\textbf{J. Sieker and T. Solstad.} Projective variability of (semi) factive verbs in family of sentence contexts: A rating study. \textit{AC 23}, 2022.\quad\textbullet\quad
				%
				\textbf{M. Simons, D. Beaver, C. Roberts, and J. Tonhauser.} The best question: Explaining the projection behavior of factives. \textit{Discourse processes}, 2017.\quad\textbullet\quad
				%
				\textbf{E.A. Smith and K.C. Hall.} The relationship between projection and embedding environment. \textit{CLS 48}. 2014.\quad\textbullet\quad
				%
				\textbf{P.F. Strawson.} On referring. \textit{Mind}, 1950.\quad\textbullet\quad
				%
				\textbf{J. Tonhauser.} Prosodic cues to presupposition projection. In \textit{SALT}, 2016.\quad\textbullet\quad
				%
				\textbf{J. Tonhauser, D.I. Beaver, and J. Degen.} How projective is projective content? Gradience in projectivity and at-issueness. \textit{JoS}, 2018.\quad\textbullet\quad
				%
				\textbf{R.A. v.d.Sandt.} Presupposition projection as anaphora resolution. \textit{JoS}, 1992.
